NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-06-20 paper/itemizedReviewResponse.tex

Q27, The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.

A: We have revised the video and include voice over and an simple introduction in the begninning.

------------------------------- Reviewer 4 -------------------------------

Q28, I was confused by the distinction between image networks and language networks. CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide "clear meaning" and seem like they would also benefit from the proposed work. In other words, I understand the focus on NLP tasks, but the reasoning for it doesn't seem accurate (in the 3rd paragraph of the introduction).

A: In the introduction we want to highlgith the input modality different. Continuous for image, and discrete for natural language. The different has introduced additional challenge especially regarding optimization as well as interpretation. In addition, in CNN we often can reveal human interpretable neuron filter, but these method has been generalized for NLP. The attention is the exception, which represent often the only interpretable part of the model.

Q29, It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs. If it's the former (as it seems to be), then I think this needs to be emphasized in the introduction.

A: The perturbation of nous and verbs on itself is not novel from NLP perspective, and truly solving the challenge of producing grammarly correct and meaningful perturbation/paraphrasing is still an open research area. In our case, we believe the novality come from the integration of the model with the three stage perturbation scheme in an explorable visual analytic system.

Q30, I appreciated the task analysis in section 4. However, it seems a bit too brief, and the tasks don't seem to directly follow from the description of the authors experience with the NLP researchers. The scenarios described in Section 6 provide much more detail about these tasks, and Section 5 clarifies them as well, but a bit more detail here would be useful. For example, it's not clear who the NLP researchers are, how many of them were interviewed, what type of NLP projects they were working on, etc.

@@

Q32, Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4). I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model. Work by Forbes et al. supports the use of semantic hypergraphs to provide richer textual annotations alongside text sequences ("Text annotation graphs: Annotating complex natural language phenomena? from LREC 2018).

A: agree, point out the interesting direction [graph anotation] linear + graph structure

Q33, In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile? with ?heap?). This updates the system and changes the inference output. Are the successful results of such an interaction remembered by the system? That is, could NLIZE be used to tweak/update the model so that, say, the ambiguity between pile and heap is automatically and more accurately resolved in future queries?

A: In the current system, we did not record the user interaction/correction result. The mira optimization update may correct the model for the given example (to some extend overfit to the example), however, we don't think there is guarantee that the fix can be easily generalized to other examples. In addition, the ambiguity between pile and heap may also originated from the word embedding (the input numerical representation for words). What the proposed system do is to communicate to the NLP experts that the ambiguity between pile and heap is likely the cause of the wrong prediciton. The experts can chose to dive further and examine the problem with their NLP background.

@@

Q34, Section 6.3 is very interesting, but I don't understand why perturbing the attention stage has less of an effect that the other perturbations. This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.

A: NLP question, further explore NLP

Q35, The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach. It might make more sense to focus more on only one or two scenarios and cover them in more depth.

A: We added a overview in the begining of the section 6 to illustrate how different tasks related to one another and provide addtional discussion on section 6.3.

### 2018-06-20 paper/intro.tex
update response letter

Compared to image classification tasks, natural language processing (NLP) systems have innate restrictions (e.g., the discrete nature of words) that make the road to interpretation even more challenging.
For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
An image (pixel values) represents a continuous solution space, in which human can quickly recognize the existence (or the absence) of patterns or shapes.
For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.
%
These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivates the proposed work.

>>>>

Compared to image classification tasks, natural language processing (NLP) systems often involve additional challenges such as the discrete nature of words.
For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
\shusen{
An image (pixel values) corresponds to a continuous solution space. which is more accessable for optimization and human visual recognation (i.e., the existence or the absence of patterns).
For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
%
These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivates the proposed work.
